\papertitle

### 2014-03-17 final-report/paper.tex
Small things and added d3 citation

% What is myria, how does it work (look at report from last quarter but shorter), which languages are supported
% motivation
% questions
% why is a visualization a good way to answer the questions

@@

\system's architecture (Fig.~\ref{fig:arch}) consists of a back-end,
used as a plug-in interface for the distributed database system targeted, and a
front-end which implements the views described above. The front-end and
back-end of \system are highly decoupled so that it can be used not only with
Myria but also with other systems such as Spark or Hadoop. In
Section~\ref{sec:back} we illustrate how we implemented log collections and
aggregation in Myria.

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3 to delive an interactive visualization experience to the user. D3 is a JavaScript framework for data visualziation on the web. We used visualization techniques such as \emph{focus+context} that possible to implement conveniently using D3.

>>>>

% What is myria, how does it work (look at report from last quarter but shorter), which languages are supported
% motivation
% questions (inspiration: https://docs.google.com/a/uw.edu/document/d/1Syn65bu_p6S4RQETaozsleYcRBauQJ7IduYrctS1wrw/edit?pli=1#)
% why is a visualization a good way to answer the questions

@@

\system's architecture (Fig.~\ref{fig:arch}) consists of a back-end,
used as a plug-in interface for the distributed database system targeted, and a
front-end which implements the views described above. The front-end and
back-end of \system are highly decoupled so that the visualization can be used not only with
Myria but also with other systems such as Spark or Hadoop. In
Section~\ref{sec:back} we illustrate how we implemented log collections and
aggregation in Myria.

@@

The Myria web front-end server is written in Python and runs on Google App Engine. \system's user-interface (UI) is embedded into Myria's web front-end. We build \system's UI using D3\cite{2011-d3} to deliver an interactive visualization experience to the user. D3 is a JavaScript framework for data visualziation on the web. We used visualization techniques such as \emph{focus+context} that possible to implement conveniently using D3.
